\sysfull

### 2017-08-11 paper/intro.tex
added anonymized link

In this work we develop {\bf \sys}: a new programming and execution model efficiently executing tasks which avoids non-termination across a range of energy buffer sizes, without burdening the programmer. To accomplish this, \sys introduces new capabilities:

@@

We evaluated \sys end-to-end on a collection of existing benchmarks ~\cite{chain} and new programs, and compare directly to a state-of-the-art task-based runtime~\cite{chain}, showing that \sys has high performance and can flexibly target a variety of platforms without rewriting code. %\todo{add detailed text about evaluation results}{Przemek}

>>>>

In this work we develop {\bf \sys}: a new programming and execution model efficiently executing tasks which avoids non-termination across a range of energy buffer sizes, without burdening the programmer\footnote{Available via \href{http://anonymized.link}{http://anonymized.link}.}. To accomplish this, \sys introduces new capabilities:

@@

We evaluated \sys end-to-end on a collection of existing benchmarks ~\cite{chain} and new programs, and compare directly to a state-of-the-art task-based runtime~\cite{chain}, showing that \sys has high performance and can flexibly target a variety of platforms without rewriting code.
